---
title: "Reaching Future Hospitality Leaders"
subtitle: "Collins College Enrollment & Retention · AO4 Proposal Presentation"
author: "Jake Evans"
institute: "IBM 6500, Cal Poly Pomona"
date: "`r Sys.Date()`"
format:
  revealjs:
    theme: [serif, custom.scss]
    width: 1600
    height: 900
    logo: images/ao4-badge.svg
    footer: "CEP Group 3 · Digital Channels & Inquiry (AO4)"
    transition: slide
    transition-speed: default
    incremental: false
    toc: true
    toc-depth: 1
    toc-title: "Roadmap"
    slide-number: true
    scrollable: true
    smaller: true
    code-fold: false
    code-overflow: wrap
    code-copy: true
    number-sections: false
    number-depth: 5
    embed-resources: true
    preview-links: auto
    css: styles.css
bibliography: references.bib
editor: visual
execute:
  echo: true
  freeze: auto
  warning: false
  message: false
---

```{r}
#| label: setup
#| echo: false

library(tidyverse)
library(knitr)

# Evidence base coded from Progress Report 1 (Evidence Matrices A and B)
evidence <- read_csv("data/ao4_evidence.csv", show_col_types = FALSE)

# College enrollment figures from the Chapter 1 group presentation
enrollment <- tibble(
  year     = c("2015–16", "2025–26"),
  students = c(1204, 434)
)

n_sources   <- nrow(evidence)
n_support   <- sum(evidence$matrix == "Supporting")
n_challenge <- sum(evidence$matrix == "Challenging")
n_inquiry   <- sum(evidence$measures_inquiry)
n_us        <- sum(str_detect(evidence$setting, "^US"))
n_since2020 <- sum(evidence$year >= 2020)

enroll_start <- enrollment$students[1]
enroll_now   <- enrollment$students[2]
pct_change   <- round((enroll_now - enroll_start) / enroll_start * 100)
dean_goal    <- 600
gap_to_goal  <- dean_goal - enroll_now
```

# Introduction {background-color="#1e4d2b"}

## Background & Business Problem

:::::::: columns
::::: {.column width="45%"}
::: card
[`r format(enroll_start, big.mark = ",")` → `r enroll_now`]{.stat}

[CCHM enrollment, 2015–16 to 2025–26 (`r pct_change`%)]{.stat-label}
:::

::: card
[\~28,000]{.stat}

[Cal Poly Pomona enrollment overall: relatively steady]{.stat-label}
:::
:::::

:::: {.column width="55%"}
The decline is **college-specific**, not campus-wide.

. . .

Strong, under-communicated assets:

::: incremental
- PolyX teaching restaurant built into the curriculum
- Wine, spirits & beer courses; wine auditorium & library
- Off-campus industry visits and a SoCal alumni network
- Dean's Board of Advisors of industry executives
:::
::::
::::::::

::: notes
The decline is college-specific. CPP overall is flat, so this isn't a campus-wide trend. The assets exist; they just aren't reaching prospects or engaging current students. The numbers on the left are pulled from the data with inline code, not typed in.
:::

## Problem Statement

Two connected problems:

::: incremental
- **Attract:** fewer new students, and the college's channels don't consistently showcase what makes CCHM unique
- **Retain:** many current students have limited involvement outside class
:::

. . .

> Enrollment and retention are one connected problem: the experiences that keep current students engaged are the same ones we promote to prospects.

## Project Objectives

::::::::: columns
:::: {.column width="33%"}
::: card
**PO1 · Enrollment**

Grow CCHM toward the Dean's goal of **\~`r dean_goal` students**, about +`r gap_to_goal` from today.
:::
::::

:::: {.column width="33%"}
::: card
**PO2 · Retention**

Raise engagement and sense of belonging, especially among first-time freshmen.
:::
::::

:::: {.column width="33%"}
::: card
**PO3 · Awareness**

Increase prospective-student awareness through content tied to campus and industry events.
:::
::::
:::::::::

## Four AOs Across the Student Journey {transition="zoom-in fade-out" transition-speed="slow"}

| Stage | Framework | Analytics Objective | Owner |
|:--------------|:--------------|:----------------------------|:--------------|
| Predisposition & search (pre-application) | Hossler & Gallagher, phases 1–2 | **AO4** · Which digital channels and content themes generate awareness and inquiry | Jake Evans |
| Choice (application → enrollment) | Hossler & Gallagher, phase 3 | **AO3** · Courses most associated with attrition and retention | Aldo Naranjo |
| Persistence (enrolled students) | Tinto's Student Integration Model | **AO1** · Belonging content and retention | Ruben Garcia |
| Persistence (enrolled students) | Tinto's Student Integration Model | **AO2** · Transfer vs. first-time freshman retention | Nik Sahami |

::: aside
This slide zooms in and fades out. Transitions can be set per slide in the heading's curly brackets.
:::

## AO4: The Analytics Objective

::: r-fit-text
Which **digital channels** and **content themes**

most effectively generate prospective-student

**awareness and inquiry** for the Collins College?
:::

## Why It Matters

::: incremental
- Inquiry is the **first observable sign of interest**: the top of the enrollment funnel PO1 depends on
- Every later stage (application, admission, enrollment) is drawn from the inquiry pool
- The college has limited marketing resources, so knowing **what to post and where** is worth more than posting more[^1]
- The first UTM-tagged campaign post is planned for **October 8, 2026**
:::

[^1]: Lund (2019) found posting volume had a negligible correlation with engagement across 50 universities.

# Literature Review {background-color="#1e4d2b"}

## Well-Established Models

::::::: columns
:::: {.column width="50%"}
::: card
**Three-phase model of college choice**

@hossler1987: predisposition → search → choice.

AO4 sits in phases 1–2, before a student applies. The model explains *where* inquiry happens in the decision process.
:::
::::

:::: {.column width="50%"}
::: card
**Content coding + proportional engagement**

@peruta2018: 17 content categories, 7 formats, and engagement ÷ followers.

Fills the gap the college-choice model leaves: *which* messages move a student from awareness to inquiry.
:::
::::
:::::::

::: notes
Hossler and Gallagher place AO4 in the decision process; Peruta and Shields give a practical way to measure and compare content for a small account like ours.
:::

## Evidence Supporting the Approach

::: incremental
- **Content matters.** Content category, format, and timing all predicted engagement across 5,932 posts [@peruta2018]
- **The website is the stable core channel.** 90.3% of students used the official .edu site [@shields2019]
- **Authentic beats promotional.** Curriculum and day-in-the-life content rated most impactful [@ozelie2025]
- **Effects show up early.** Social media is most influential at the initial-interest stage [@delosreyes2023]
- **A comparable design exists.** One department, 58 posts, IRB-exempt public data [@mishnick2024]
:::

## Evidence Challenging the Approach

- [Posting volume ≈ no effect; prestige and endowment dominate [@lund2019]]{.fragment .fade-up}
- [Social media's value rose mainly when in-person channels closed [@ng2023]]{.fragment .fade-up}
- [Students and third parties generate most messaging about a school [@belanger2014]]{.fragment .fade-up}
- [Paid search can't buy past low brand recognition [@taylor2020]]{.fragment .fade-up}
- [Website effects may work only through mediators like usability [@eveleth2015]]{.fragment .fade-up}

. . .

[Takeaway: *what* we post matters more than *how much*, and effects will be modest.]{.fragment .highlight-red}

## Adequacy of the Gathered Evidence

```{r}
#| label: coverage-chart
#| echo: true
#| code-fold: true
#| code-summary: "Show the chart code"
#| fig-width: 11
#| fig-height: 4.6
#| fig-align: center

coverage <- evidence |>
  pivot_longer(starts_with("iv_"), names_to = "iv", values_to = "covered") |>
  filter(covered) |>
  mutate(iv = recode(iv,
                     iv_channel = "Channel & medium",
                     iv_theme   = "Content theme",
                     iv_format  = "Creative format",
                     iv_timing  = "Publication timing")) |>
  count(iv, matrix)

ggplot(coverage, aes(x = n, y = fct_reorder(iv, n, .fun = sum), fill = matrix)) +
  geom_col(width = 0.65) +
  scale_fill_manual(values = c(Supporting = "#1e4d2b", Challenging = "#c99700")) +
  scale_x_continuous(breaks = 0:10, expand = expansion(mult = c(0, 0.05))) +
  labs(x = "Number of sources", y = NULL, fill = NULL,
       title = "Which AO4 independent variables does the evidence base address?") +
  theme_minimal(base_size = 18) +
  theme(legend.position = "top", panel.grid.major.y = element_blank())
```

::: gap
Of `r n_sources` sources reviewed (`r n_support` supporting, `r n_challenge` challenging), **`r n_inquiry` measure inquiry** as the outcome. Only `r n_us` are U.S.-based, and `r n_since2020` were published since 2020.
:::

::: notes
Every number in the green box is inline R code reading the evidence file. If I add a source to the CSV, the chart and the sentence both update on render. Channel is well covered; publication timing rests on a single study.
:::

## What the Studies Actually Measured {.scrollable}

```{r}
#| label: outcomes-table
#| echo: false

evidence |>
  count(outcome_type, name = "Sources") |>
  arrange(desc(Sources)) |>
  rename(`Outcome measured` = outcome_type) |>
  kable()
```

. . .

None of these is **inquiry**. @cingillioglu2024 found the same across 43 articles: inquiry is a genuine gap in the literature, not a limit of the search.

## Need for Additional Analysis

- [**GA4 pre-campaign baseline**: published research can't tell us the college's current channel performance]{.fragment .highlight-gold}
- [**Behavioral data first**: GA4 and platform analytics as primary evidence; the IRB survey explains *why*]{.fragment .highlight-gold}
- [**Control for the application cycle**: seasonal demand is the main competing explanation]{.fragment .highlight-gold}
- [**Sharpen the DV**: form submissions and portal referrals weigh above softer signals]{.fragment .highlight-gold}

::: notes
These four gold highlights use a custom fragment class defined in styles.css.
:::

# Methods {background-color="#1e4d2b"}

## Data and Sampling

::::: columns
::: {.column width="50%"}
**Primary data**

- GA4 with consistent UTM tagging (access via Taylor Uster, Collins Marketing Communications)
- Platform analytics: Facebook, Instagram, X/Twitter, YouTube
- Email and paid advertising metrics
- IRB-approved prospective-student survey
:::

::: {.column width="50%"}
**Sampling frame**

- Unit of analysis: each **campaign post** (or campaign day)
- Window: Fall 2026 – Spring 2027 campaign; analysis Summer 2027
- Every post tagged so inquiries link back to the post that produced them
- **Secondary:** aggregate application, admission, and enrollment counts before vs. after the campaign
:::
:::::

## Data Wrangling

The evidence base is coded as one row per source. Reshaping it long lets us count coverage by independent variable:

```{r}
#| label: wrangle-demo
#| echo: true
#| code-line-numbers: "|1-2|3|4-8|9"
#| output-location: fragment

evidence |>
  pivot_longer(starts_with("iv_"), names_to = "iv", values_to = "covered") |>
  filter(covered) |>
  mutate(iv = recode(iv,
                     iv_channel = "Channel & medium",
                     iv_theme   = "Content theme",
                     iv_format  = "Creative format",
                     iv_timing  = "Publication timing")) |>
  count(iv, matrix)
```

::: notes
Click through: line highlighting walks the audience through the pipeline, and the output appears only after the last step, like running it live.
:::

## Sample Characteristics (Evidence Base)

```{r}
#| label: sample-table
#| echo: false

evidence |>
  arrange(matrix, year) |>
  transmute(Source = paste0(source, " (", year, ")"),
            Matrix = matrix,
            N = format(sample_n, big.mark = ","),
            Unit = sample_unit,
            Setting = setting) |>
  mutate(N = if_else(str_trim(N) == "NA", "n/r", N)) |>
  kable()
```

::: aside
Campaign data are not yet collected; this table describes the published evidence. n/r = not reported.
:::

## Measures

| Role | Construct | Operationalization |
|:---------------|:-------------------|:-----------------------------------|
| **DV (primary)** | Inquiry | Intake form submissions, Bronco Applicant Portal referrals |
| **DV (secondary)** | Inquiry | Engaged program-page sessions, event registrations, email sign-ups |
| **IV** | Channel & medium | Platform; organic, paid, email, or referral traffic |
| **IV** | Content theme | Main subject of the post or page |
| **IV** | Creative format | Static image, carousel, short-form video, text |
| **IV** | Publication timing | Day of week and time of day |
| **Offset** | Reach | Impressions per post |

## Analytics Methods

::: incremental
1.  **Primary: negative binomial regression** on post-level inquiry counts, with channel and content theme as main predictors, controlling for timing and reach
2.  **Fallback:** if posts are too few, nonparametric group comparisons with effect sizes [following @peruta2018], plus descriptive GA4 channel contribution
3.  **Secondary funnel:** application→admission and admission→enrollment rates compared before vs. after with **χ² tests and φ** [following @delosreyes2023], periods matched to the same point in the cycle [@ng2023]
:::

. . .

::: card
Realistic expectations: a comparable department drew **fewer than five engagements per post** [@mishnick2024].
:::

# References {background-color="#1e4d2b"}

## References {.scrollable}

::: {#refs}
:::

# Appendix {background-color="#1e4d2b" visibility="uncounted"}

## Links {visibility="uncounted"}

- [CEP Group 3 project site](https://jakevns.github.io/cep-group3-collins-enrollment-retention/)
- [AO4 Progress Report 1 (PDF)](https://jakevns.github.io/cep-group3-collins-enrollment-retention/assignments/progress-reports/AO4-progress-report-1.pdf)
- [Chapter 1 + Section 2.7 group presentation](https://jakevns.github.io/cep-group3-collins-enrollment-retention/assignments/progress-reports/ch1-sec27-presentation.html)
- [Quarto Reveal.js documentation](https://quarto.org/docs/presentations/revealjs/)
- [CCIDM effective-quarto-slides repo](https://github.com/CCIDM/effective-quarto-slides)
- [Case 31 sample presentation](https://jmjung.quarto.pub/case31-presentatoin/)

::: aside
Press **S** for speaker notes, **F** for full screen, **Esc** for overview, **Alt/Option + click** to zoom.
:::
