---
title: "R Markdown: Reproducible Report in Data Science"
author: "Jake"
date: "`r Sys.time()`"
output: 
  html_document:
    toc: yes
    toc_depth: 4
    toc_float:
      collapsed: false
    highlight: espresso
    theme: journal
    number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# R Markdown

R Markdown is a format for writing reproducible, dynamic, reports with R. Use it embed R code and results into slideshow, pdfs, html documents, Word files and mroe.

# Structure

1.  YAML Header
2.  Text Area
3.  Code Chunk

# WorkFlow

1.  Open - Open a file that uses the .Rmd extension.
2.  Write - Write content with the easy to use R Markdown syntax.
3.  Embed - Embed R code that creates output to include in the report.
4.  Render - Replace R code with its output and transform the report into a slideshow, pdf, html, or ms word file.

# Text Area Formatting Tooks:

Plain Text

End a line with two spaces to start a new paragraph.

*italic* and *italics* **bold** and **bold** superscript^2^ ~~strikethrough~~ Hyperlink: [CCIDM](https://www.cpp.edu/cba/customer-isnights-lab/index.shtml)

# Header 1

## Header 2

### Header 3

#### Header 4

##### Header 5

###### Header 6

emdash: -- emdash: --- inline equation: $A = \pi*r^2$ slide break:

------------------------------------------------------------------------

> Block quote

1.  Odered list 1
2.  Ordered list 2
    - sub-item 1
    - sub-item 2

| Table Header | Second Header |
|:------------:|--------------:|
|  Table Cell  |        Cell 2 |
|    Cell 3    |        Cell 4 |

# YAML Header

> A YAML Header is a set of key: value pairs at the start of your file. Begin and end the header with the line of three dashes (---). (From the rmd Cheatsheet <https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf>)

You will notice that *my YAML header* is difference from the default one Rmd file automatically created. That is because I Customized output option as aboe. This setting dictates how your html file that will be knitted will look like.

- **date**: '`r format(Sys.time())`' -This allows to print the current time each time you knit the file.\
  -Can be customized in various ways
  - date-time: '`r Sys.time()`"
  - Day, Month, Date, Year (e.g. Tuesday, Feburary 10, 2023): '`r format(Sys.time(),"%A, %B, %d, %Y")`'
  - m/d/y (e.g., 10/15/2023): '`r format(Sys.time(),  "%m/%d/%Y")`'

------------------------------------------------------------------------

- **toc**: yes
  - I Turned the table of contents on.  This will ahve hyperlinsk in HTML and allow readers to navigate the desired sections faster. 
- **toc_depth**: 4
  - I want to see up to four levels of headings
- **toc_float**: true
  -adding this move toc from the front end fo teh document to a left side floating when you scroll it down. 
  -By Default, the floating toc headings are collapsed, not showing all headings.  We can turn it off using the following.
  ```
  toc_float:
    collapsed: false
  ```
-**highlight**: espresso
  -I want to see "espresso" style: black background of codes area.
- **theme**: journal 
  -journal style. Choose the style you like. 
- **number_sections**: yes
  -turned on automatic setion numbering, which is why I didn't add numbering manually below. 
    -notice hwo this will nicely turn your HTML report much mroe organized. 
  -Try this and other options to see which one you like the most in your HTML file. 
    
# Embed Codes

## Code Chunk

### Sample

* Ctrl + alt + I

```{r penguins}

# use ctrl + Enter at the same time to execute a line. 
# Use # to comment out a code
# install.packages("tidyverse")
library(tidyverse)

#install.packages("palmerpenguins")
library("palmerpenguins")
penguins

dim(penguins)
skimr::skim(penguins)

# Sex Distribution
penguins %>%
  count(sex) %>%
  ggplot(aes(sex, n)) +
  geom_col()

# Number of male
sum(penguins$sex == "male", na.rm = TRUE)

# Total Observation
nrow(penguins)

# Percent of Males
m_per <- round((sum(penguins$sex == "male, na.rm = TRUE") / nrow(penguins)) * 100, digits = 1)

# Percent of Females
f_per <- round((sum(penguins$sex == "female, na.rm = TRUE") / nrow(penguins)) * 100, digits = 1)

```

## Code chunk options

For more details visit <https://vihui.org/knitr/options>

## Inline Coding 

* Sample Characteristics: 
There are `r nrow(penguins)` penguins in the data, `r m_per` % of which are male and `r f_per` ^ of which are females.  

# Navigation

* Outline (right side)
* Status Bar (bottom)

#  Expectations for ORganizing your Assignment report with Rmd File.  
## M01-1 Principle Assignment

# References 

Markdown Cheatsheet <https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf>